Canonical rings of rational divisors on projective space and Hirzebruch surfaces

### 2015-07-16 surfaces-write-up/surface-write-up.tex
intro add relation to curve canrings, add lrz to bib

Voight and Zureick-Brown \cite[Proposition 6.1.5]{vzb:stacky}, which allows one to translate the analytic category of 1-dimensional complex orbifolds to the algebraic category of stacky curves. 
We expect that  will similarly allow one to generalize yield an eqivalence of categories between an appropriate subcategory of $m$-dimensional orbifolds and a subcategory of $m$-dimensional algebraic spaces.
In particular, this will allow us to translate rings of Hilbert Modular forms and Siegel modular forms whose underlying space is isomorphic to $\bp^m$ or a Hirzebruch surface to canonical rings on the corresponding algebraic surfaces. Thereby, our techniques would give a bound on generators and relations for Hilbert and Siegel modular forms with certain underlying spaces.
\todo{include references}

Another closely related topic is the Hassett-Kell program 
initiated in \todo{ was it actually initiated here? check vzb.} \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form
\begin{align*}
	\overline {\mathscr M}_g(\alpha) := \oplus_{d \geq 0}H^0 \left( \overline {\mathscr M}_g, \lfloor d K_{\overline{\mathscr M}_g} + \alpha\delta \rfloor  \right) 
\end{align*}
in terms of certain moduli spaces. Fractional divisors on surfaces also naturally appear when considering the canonical ring of surfaces of kodaira dimension 1. A surface has Kodaira dimension 1 if and only if it is an elliptic surface, and their canonical ring are most naturally described in the setting of fractional divisors. \todo{Add references}

>>>>

By a result by Voight and Zureick-Brown \cite[Proposition 6.1.5]{vzb:stacky}, one can translate the analytic category of 1-dimensional complex orbifolds to the algebraic category of stacky curves. 
We expect that  will similarly allow one to generalize yield an eqivalence of categories between an appropriate subcategory of $m$-dimensional orbifolds and a subcategory of $m$-dimensional algebraic spaces.
In particular, this will allow us to translate rings of Hilbert Modular forms and Siegel modular forms whose underlying space is isomorphic to $\bp^m$ or a Hirzebruch surface to canonical rings on the corresponding algebraic surfaces. Thereby, our techniques would give a bound on generators and relations for Hilbert and Siegel modular forms with certain underlying spaces.
\todo{include references}

Another closely related topic is the Hassett-Keel program 
initiated in \todo{ was it actually initiated here? check vzb.} \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form
\begin{align*}
	\overline {\mathscr M}_g(\alpha) := \oplus_{d \geq 0}H^0 \left( \overline {\mathscr M}_g, \lfloor d K_{\overline{\mathscr M}_g} + \alpha\delta \rfloor  \right) 
\end{align*}
in terms of certain moduli spaces. Fractional divisors on surfaces also naturally appear when considering the canonical ring of surfaces of kodaira dimension 1. A surface has Kodaira dimension 1 if and only if it is an elliptic surface, and their canonical ring are most naturally described in the setting of fractional divisors. \todo{Add references}

Furthermore, this work extends the study of canonical rings of
$\bq$-divisors on curves, as done by O'Dorney \cite{dorney:canonical},
Voight--Zureick-Brown \cite{vzb:stacky}, and Landesman--Ruhm--Zhang
\cite{lrz:spin-cring}, to general projective space and Hirzebruch
surfaces.

\todo{more!}
